systemfit: A Package to Estimate\\ Simultaneous Equation Systems in \proglang{R}

### 2006-02-18 paper/trunk/systemfit_intro.tex
substituted "covariance matrix" for "variance-covariance matrix" and "\Cov [ . ]" for "Var [ . ]", where "\Cov" is a command for "\text{Cov}"
git-svn-id: svn://svn.r-forge.r-project.org/svnroot/systemfit@605 591db2bd-e0a0-4d22-8c19-2192dbb7da31
considerably revised introduction
git-svn-id: svn://svn.r-forge.r-project.org/svnroot/systemfit@609 591db2bd-e0a0-4d22-8c19-2192dbb7da31

Many theoretical models consist of more than one equation.
These models can contain variables that appear on the left-hand side in one
equation and on the right-hand side of another equation (simultaneity-bias).
The system can have non-zero off-diagonal covariance elements resulting from
related disturbances (contemporaneous correlation).
Ignoring contemporaneous correlation leads to inefficient parameter
estimates \citep{zellner62} and ignoring simultaneity-bias can lead to
inconsistent parameter estimates.

% If these models are econometrically estimated, it may not be
% appropriate to estimate the equations individually, but all together,
% because the disturbance terms of these equations are likely to be
% contemporaneously correlated.  Estimating all equations
% simultaneously, taking the covariance structure of the residuals into
% account, leads to efficient estimates.  Ignoring this correlation
% leads to an inefficient parameter estimation \citep{zellner62}.

Another reason to estimate an equation system simultaneously are
cross-equation parameter restrictions.
These restrictions can be tested and/or imposed only in a simultaneous
estimation approach.
Especially the economic theory suggests many cross-equation parameter
restrictions (e.g.\ the symmetry restriction in demand models).

% (But we don't say why this is important...) Are we
% imposing restrictions in the parameters, or the variance-covariance
% matrix or both and for what pupose?

% For all of the methods developed in the package, the disturbances of
% the individual equations are assumed to be independent and identially
% distributed (iid).  
% In the future, we would like to add the ability to fit equations were
% the disturbances are serially correlated (wikins 1969).

@@

This paper is organized as follows: In Section~\ref{sec:Estimation} we
introduce the mathematics of estimating equation systems.
Section~\ref{sec:Restrictions} shows how linear restrictions can be
imposed.
Section~\ref{sec:Usage} demonstrates how to run
\pkg{systemfit}, especially how the features presented in the previous
sections can be used.
All other relevant issues are discussed in Section~\ref{sec:Other}.
Finally, a summary and outlook are presented in
Section~\ref{sec:Summmary}.

>>>>

Many theoretical models that are econometrically estimated
consist of more than one equation.
In this case, the disturbance terms of these equations are likely
to be contemporaneously correlated,
because some unconsidered factors
that influence the disturbance term in one equation
probably influence the disturbance terms in other equations
of these model, too.
Ignoring this contemporaneous correlation
and estimating these equations separately
leads to inefficient parameter estimates.
However, estimating all equations simultaneously,
taking the covariance structure of the residuals into account,
leads to efficient estimates.
This estimation procedure is generally called
°Seemingly Unrelated Regression° (SUR) \citep{zellner62}.
Another reason to estimate an equation system simultaneously are
cross-equation parameter restrictions.%
\footnote{
Especially the economic theory suggests many cross-equation parameter
restrictions (e.g.\ the symmetry restriction in demand models).
}
These restrictions can be tested and/or imposed only in a simultaneous
estimation approach.

Furthermore, these models can contain variables
that appear on the left-hand side in one equation
and on the right-hand side of another equation.
Ignoring the endogeneity of these variables can lead to inconsistent
parameter estimates.
This simultaneity bias can be circumvented by applying
a °Two-Stage Least Squares° (2SLS) or °Three-Stage Least Squares° (3SLS)
estimation of the equation system.

% For all of the methods developed in the package, the disturbances of
% the individual equations are assumed to be independent and identically
% distributed (iid).  
% In the future, we would like to add the ability to fit equations were
% the disturbances are serially correlated (wikins 1969).

@@

This paper is organized as follows:
In the following Section~\ref{sec:Estimation} we
introduce the mathematics of estimating equation systems.
Section~\ref{sec:Restrictions} shows how linear restrictions can be
imposed.
Some other relevant issues about estimation of equation systems
are discussed in Section~\ref{sec:Other}.
Section~\ref{sec:Usage} demonstrates how to run
\pkg{systemfit}, especially how the features presented in the previous
sections can be used.
Finally, a summary and outlook are presented in
Section~\ref{sec:Summmary}.
